---
title: "Tables"
author: "Matija"
date: '19 srpnja 2017 '
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE,echo=FALSE,warning=FALSE,results='hide'}
setwd("..")
source("mainHeader.R",encoding = "UTF-8")
library(knitr)
```
#Review Articles

```{r reviewArticlesTable, results='asis', echo=FALSE}
kable(apya$createTableOfAllAnalysisArticles(mydata.filtered))
```

##Review Articles Missing Added manualy

```{r reviewArticlesMissingTable, results='asis', echo=FALSE}
kable(apya$createTableOfAllAnalysisArticles(mydata.filteredOnlyManualForReview))
```

#Top  tools usage

```{r topToolsUsage, results='asis', echo=FALSE}
kable(pdta$getTableMinAndMaxYearUsingATool(mydata.filtered,topTools))
kable(pdta$listArticlesThatUseTools(mydata.filtered,c("jPlag","MOSS","SIMfromGrune","Plaggie","SherlockWarwick")))
```

# Algorithm analysis
##1 standardAlgorithmCategorization

```{r standardAlgorithmCategorization, results='asis', echo=FALSE}
prepareTableHeader <- function(table){
    dfm <- DataFrameMaipulator$new()
    table <- dfm$changeColumnNameInDataFrame(table,"Algorithm_or_Algorithm_Type","Algorithm Type")
    table <- dfm$changeColumnNameInDataFrame(table,"All","Number of articles")
    table <- dfm$changeColumnNameInDataFrame(table,"firstYear","First year")
    table <- dfm$changeColumnNameInDataFrame(table,"lastYear","Last year")
}
printTable <- prepareTableHeader(aasma$getTableMinAndMaxYearUsingAlgorithm(mydata.filtered.devTool,standardAlgorithmCategorization))
kable(printTable)
```

##2 newAlgorithmCategorization

```{r newAlgorithmCategorization, results='asis', echo=FALSE}
printTable <- prepareTableHeader(aasma$getTableMinAndMaxYearUsingAlgorithm(mydata.filtered.devTool,newAlgorithmCategorization))
kable(printTable)
```

##3 commonAlgorithmsUsed and similairtyMeasures

```{r commonAlgorithmsUsed, results='asis', echo=FALSE}
printTable <- prepareTableHeader(aasma$getTableMinAndMaxYearUsingAlgorithm(mydata.filtered.devTool,c(commonAlgorithmsUsed,similarityMeasures)))
kable(printTable)
```

##listarticles for algorithm

```{r listarticlesforalgorithm, results='asis', echo=FALSE}
kable(aasma$listArticlesThatUseAlgorithms(mydata.filtered.devTool,allAlgorithms))
```

#articles that do some comparison

```{r comparisonArticles, results='asis', echo=FALSE}
kable(dfmHelp$createDataFrameOfPrintColumnValuesForColumns(mydata.filtered.compTools,c("ToolComparison","OnlyToolComparisons"),"AnalysisID"))
```

#comparison metircs analysis

```{r comparisonMetrics, results='asis', echo=FALSE}
kable(cma$numberOfArticlesWithMinAndMaxYearComapringAndDevelopig())
```

##articles that do some comparison by metric

```{r comparisonArticlesByMetric, results='asis', echo=FALSE}
kable(dfmHelp$createDataFrameOfPrintColumnValuesForColumns(mydata.filtered.compTools,topMetrics,"AnalysisID"))
```

##combinations of precision and recall

```{r precisionRecallCombinations, results='asis', echo=FALSE}
kable(cma$numberOfArticlesUsingPrecisionAndRecallCombinations(mydata.filtered.compTools))
```

#Dataset analysis

##numberOfArticlesUsingDatasetsTypeByDifferentArticlesIncluded

```{r datasetUsageByDifferentArticlesIncluded, results='asis', echo=FALSE}
kable(adsa$numberOfArticlesUsingDatasetsTypeByDifferentArticlesIncluded(mydata.filtered,usedDatasetTypes,c("ToolDeveloped","ToolUsedOrDeveloped","ToolCompariosonOrOnlyComparison")))
```

##comparisonArticlesByDatasetType

```{r comparisonArticlesByDatasetType, results='asis', echo=FALSE}
kable(dfmHelp$createDataFrameOfPrintColumnValuesForColumns(mydata.filtered.compTools,usedDatasetTypes,"AnalysisID"))
```

##programmingLanguages

```{r programmingLanguages, results='asis', echo=FALSE}
kable(dfmHelp$createDataFrameOfPrintColumnValuesForColumns(mydata.filtered.ducTool,programmingLanguages,"AnalysisID"))
```

##programmingLanguagesPerYear

```{r programmingLanguagesPerYear, results='asis', echo=FALSE}
kable(adsa$numberOfArticlesUsingWhichProgrammingLanguagePerYear(mydata.filtered.ducTool,top10ProgrammingLanguages))
```

##top cited articles

```{r topCitedArticles, results='asis', echo=FALSE}
kable(apya$getArticlesSortedAndFilteredByCitation(mydata.filtered,50))
```

##apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","IEEE"))

```{r articlesDatabaseCombination1, results='asis', echo=FALSE}
kable(apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","IEEE")))
```

##apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","ACM"))

```{r articlesDatabaseCombination2, results='asis', echo=FALSE}
kable(apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","ACM")))

```

##apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","ACM","IEEE")

```{r articlesDatabaseCombination3, results='asis', echo=FALSE}
kable(apya$articlesInDatabaseCombination(mydata.filtered,c("Scopus","WOS","ACM","IEEE")))
```
